---
title: "Data"
output: html_document
---

```{r setup, include=FALSE}
# switch off printing messages and warnings
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

# load libraries
library(reshape2) # for melting data frames
library(DT) # for printing nice interactive data tables
```



# Generate data

Simulate 9 angles for 30 random dinucleotids in each of 10 NtC classes.
```{r}
# define constants for simulation
ANGLE_COUNT <- 9 # number of measured angles
NTC_CLASS_COUNT <- 10 # number of NtC classes
STEP_IN_CLASS_COUNT <- 100 # number of steps in each NtC class

# names of NtC classes and angles
class_names <- paste0('C', 1:NTC_CLASS_COUNT)
angle_names <-  paste0('A', 1:ANGLE_COUNT)

# simulate uniformly distributed angles for each class and angle name
set.seed(1) # set fix seed so the simulation is the same every time
angles <- data.frame(class = rep(class_names, each = ANGLE_COUNT),
                    angle_name = rep(angle_names, times = NTC_CLASS_COUNT),
                    angle = runif(n = ANGLE_COUNT*NTC_CLASS_COUNT, min = 0, max = 180))

# replicate data several times so we have more steps in each class
angles <- angles[rep(1:nrow(angles), times = STEP_IN_CLASS_COUNT),]
angles$step_index <- rep(1:(STEP_IN_CLASS_COUNT), each = ANGLE_COUNT*NTC_CLASS_COUNT)

# add random noise to angles so it is not the same in each step
noise <- rnorm(n = ANGLE_COUNT*NTC_CLASS_COUNT*STEP_IN_CLASS_COUNT, mean = 0, sd = 10)
angles$angle <- angles$angle + noise

# save data
dir.create(paste0(getwd(), '/data')) # create subdir for data in working directory
save(list = 'angles', file = './data/angles.RData') # for later loading to R
write.table(x = angles, file = './data/angles.csv', row.names = F, 
            sep = ';', dec = '.', quote = F) # as csv
```



# Print data {.tabset}

## Data table

Print data as an interactive table with pages, sorting, filters and formatting. We see that the random noise caused that some angles are outside the $[\alpha_1, \alpha_2) = [0°, 180°)$ interval.

```{r}
# print data as nice data table
# filter on the top, pages with defaultly 10 rows, automatic column width and table caption
datatable(angles, filter = 'top', rownames = FALSE, 
          options = list(pageLength = 10, autoWidth = TRUE),
          colnames = c('Class', 'Angle name', 'Angle', 'Step index'),
          caption = 'Table: Simulated angles') %>% 
  # round numbers to two digits
  formatRound(columns = 'angle', digits = 2) %>%
  # numbers outside (0, 180) range format with red text color in each column with angles
  formatStyle(columns = 'angle', valueColumns = 'angle', 
              color = styleInterval(cuts = c(0, 180), values = c("red", "black", "red"))) %>%
  # in column with angle a add grey bars to background
  formatStyle(columns = 'angle', valueColumns = 'angle', 
              background  = styleColorBar(c(0, 180), color = "lightgrey"))
```


## Transformed data table

Transform table so there are angles in columns and print it.

```{r}
# transform data frame so we have separate column for each angle
angles <- dcast(data = angles, formula = class + step_index ~ angle_names, value.var = 'angle')

# print data as nice data table
# filter on the top, pages with defaultly 10 rows, automatic column width and table caption
datatable(angles, filter = 'top', rownames = FALSE, 
          options = list(pageLength = 10, autoWidth = TRUE, scrollX = TRUE), 
          caption = 'Table: Simulated angles') %>% 
  # round numbers to two digits
  formatRound(columns = angle_names, digits = 2) %>%
  # numbers outside (0, 180) range format with red text color in each column with angles
  formatStyle(columns = angle_names, valueColumns = angle_names, 
              color = styleInterval(cuts = c(0, 180), values = c("red", "black", "red"))) %>%
  # in column with angle A1 add grey bars to background
  formatStyle(columns = 'A1', valueColumns = 'A1', 
              background  = styleColorBar(c(0, 180), color = "lightgrey"))
```


## Classic summary statistics

Print summary statistics for the first five columns.

```{r}
s <- summary(angles[angles$class=='C1',])
knitr::kable(s)
```


## Better summary statistics

Print summary statistics for the first class as nice table.

```{r}
library(papeR)
s <- summarize(angles[angles$class=='C1',])
knitr::kable(s)
```