---
title: "Introduction"
output:  html_document

---

This is a website for plotting some randomly generated data. It was created using R Markdown (in RStudio) - a user friendly and time efficient way how to create a nice website within a few lines of R code.

# Languages
It can generate a website from text (including LaTeX) and R 
(or Python, Bash etc. if necessary) code outputs.

## R
This is an R chunk and its output.
```{r}
fruits <- c('mango', 'orange', 'apple')
for(fruit in fruits) {
  print(fruit)
}
```

## Python
This is a Python chunk and its output.
```{python}
fruits = ['mango', 'orange', 'apple']
for fruit in fruits:
  print(fruit)
```

<!-- ### Bash -->
<!-- This is a bash chunk. -->
<!-- ```{bash} -->
<!-- echo hello world -->
<!-- ``` -->


## LaTeX

This is an equation in LaTeX:

$$ e^{i \pi} + 1 = 0 $$

# R Markdown 

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
