---
title: "Plots"
output: html_document
---

```{r setup, include=FALSE}
# switch off printing messages and warnings
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

# load libraries
library(reshape2) # for melting data frames
library(ggplot2) # for creating nice plots
library(plotly) # for making static ggplots interactive
library(htmlwidgets) # for saving interactive plots
library(svglite) # for saving plots in svg format (vector graphics - quality is independent on zoom)
# library(devtools) # for installing packages from github
# install_github("walkerke/bsselectR")
library(bsselectR) # for creating menu where we can choose different plots
```


# Create plots

Load data and create plots using [ggplot2 library](http://ggplot2.tidyverse.org/index.html) for nice static plots and make them interactive
using [plotly library](https://plot.ly/).

```{r}
# load data
angles <- read.table(file = './data/angles.csv', sep = ';', dec = '.', header = T)
class_names <- unique(angles$class)
angle_names <- unique(angles$angle_name)

# create subdirs in working directory
dir.create(paste0(getwd(), '/plots')) 

# create and save plots for each NtC class
for(class in class_names) {
  # subset data for given class
  angles_plot <- angles[angles$class == class, ]
  
  # static densities
  density_plot_static <- ggplot(angles_plot, mapping = aes(x = angle, colour = angle_name)) + 
                          geom_density(adjust=2) + ggtitle(paste('NtC class:', class))
  path <- paste0("./plots/Density static [Class ", class, "].svg")
  ggsave(filename = path, plot = density_plot_static, 
         units  = 'cm', width = 15, height = 10, dpi = 300)
  
  # static histograms
  histogram_plot_static <- ggplot(angles_plot, mapping = aes(x = angle, fill = angle_name)) + 
                            geom_histogram(position = 'identity', alpha=0.2) + 
                            ggtitle(paste('NtC class:', class))
  path <- paste0("./plots/Histogram static [Class ", class, "].svg")
  ggsave(filename = path, plot = histogram_plot_static, 
         units  = 'cm', width = 15, height = 10, dpi = 300)
  
  # create interactive plots from static ggplots
  density_plot_interactive <- ggplotly(density_plot_static)
  histogram_plot_interactive <- ggplotly(histogram_plot_static)
  
  # save interactive density plots
  path <- paste0("./plots/Density interactive [Class ", class, "].html")
  # saveWidget function needs absolute path
  path <- file.path(normalizePath(dirname(path)),basename(path))  
  saveWidget(widget = density_plot_interactive, selfcontained = F, 
             libdir = './plotly_libraries', file = path)
  
  # save interactive histogram plots
  path <- paste0("./plots/Histogram interactive [Class ", class, "].html")
  path <- file.path(normalizePath(dirname(path)),basename(path))
  saveWidget(widget = histogram_plot_interactive, selfcontained = F, 
             libdir = './plotly_libraries', file = path)
}
```


# View plots {.tabset}
View created plots.

## View static histograms

Static histograms are not too clear.

```{r}
view_plots <- function(path_to_plots = './plots', plot_name_filter, type = 'img') {
  # Select all plots from folder on 'path_to_plots' that have 'plot_name_filter'
  # in the file name and view them with select option.
  # The names of the plots will be extracted as part of the file names between '[' and ']'.
  # If it is a static plot, type = 'img', if interactive type = 'iframe'.
  
  plot_paths <- list.files(path = path_to_plots, pattern = plot_name_filter, full.names = TRUE)
  plot_names <- substr(x = plot_paths, 
                       start = regexpr(text = plot_paths, pattern = "\\[")+1,
                       stop = regexpr(text = plot_paths, pattern = "\\]")-1)
  names(plot_paths) <- plot_names
  bsselect(vector = plot_paths, type = type, live_search = TRUE, show_tick = TRUE)
}

view_plots(plot_name_filter = 'Histogram static')
```


## View static densities

Static densities are a bit better.

```{r}
view_plots(plot_name_filter = 'Density static')
```


## View interactive histograms

Click or double click on any line in the legend. Select any part of the plot. 
Double click on the plot. Click on any button on the top.

```{r}
view_plots(plot_name_filter = 'Histogram interactive', type = 'iframe')
```


## View interactive densities

Hmm...

```{r}
view_plots(plot_name_filter = 'Density interactive', type = 'iframe')
```
