---
title: "Proteins"
output:
  flexdashboard::flex_dashboard:
    # vertical_layout: scroll
    vertical_layout: fill
    # orientation: rows
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(reshape2)
library(ggplot2)
library(plotly)
library(tsne)
source('../plots_library.R')
```

Introduction {data-orientation=columns}
=============================================================================

Column {data-width=600}
-----------------------------------------------------------------------------

### Flex dashboards for R

This is a dashboard created using R Markdown and `flexdashboard` library.
For more information see the [official website](http://rmarkdown.rstudio.com/flexdashboard/index.html).

Column {data-width=400}
-----------------------------------------------------------------------------

### Data

Some random stuff.

```{r}
print(paste('Hello number', 1:22))
```


### Equations

This is an equation in LaTeX:

$$ e^{i \pi} + 1 = 0 $$


Data {data-orientation=rows}
=============================================================================

Data tables with angles data.

Row {.tabset}
-----------------------------------------------------------------------------

### Data 
```{r}
# load data
angles <- read.table(file = '../data/angles.csv', sep = ';', dec = '.', header = T, stringsAsFactors = F)
class_names <- unique(angles$class)
angle_names <- unique(angles$angle_name)

# print data
datatable(angles, filter = 'top', options = list(paging = FALSE)) %>%
  formatRound(columns = 'angle', digits = 2)
```

> This are our data in the original format.

### Transformed data
```{r}
# transform data frame so we have separate column for each angle
angles_transformed <- dcast(data = angles, formula = class + step_index ~ angle_names, value.var = 'angle')
datatable(angles_transformed, filter = 'top', options = list(paging = FALSE)) %>%
  formatRound(columns = angle_names, digits = 2)
```

> This are transformed data with angles in columns.

Plots 
=============================================================================

Plots with angles data.

Row {.tabset}
-----------------------------------------------------------------------------

### Densities
```{r}
view_plots('../plots', 'Density interactive', 'iframe')
```

> These are the interactive density plots which we generated before.

### Histogram
```{r}
ggplotly(ggplot(angles[angles$class == 'C1',], mapping = aes(x = angle, colour = angle_name)) + geom_histogram(position = 'identity', alpha = 0.2) + ggtitle('Class C1'))
```

> These are histograms for class C1.

### Boxplots
```{r}
ggplotly(ggplot(angles, mapping = aes(y = angle, x = angle_name, col = class)) + geom_boxplot())
```

> These are boxplots.

### Violin plots
```{r}
p <- ggplot(angles, mapping = aes(y = angle, x = angle_name, col = class)) + 
  geom_violin(position=position_dodge(0)) + 
  stat_summary(fun.y = "median", geom = "point")
  # stat_summary(fun.data=mean_sdl, mult=5, geom="pointrange")
ggplotly(p)
```

> These are violin plots with medians.


t-SNE 
=============================================================================

This is the outcome from an application of t-SNE algorithm on the angles data. 

Row 
-----------------------------------------------------------------------------

### t-SNE algorithm

```{r}
angles_matrix <- as.matrix(angles_transformed[3:ncol(angles_transformed)])

# identify clusters and add informations about them to the result 
# clusters <- tsne(angles_matrix, max_iter = 200)
# clusters_info <- as.data.frame(clusters)
# colnames(clusters_info) <- c('x_tsne_coordinate', 'y_tsne_coordinate')
# clusters_info <- cbind(angles_transformed, clusters_info)

# save the result of the algorithm so it is not recalculated every time
# save(file = '../data/clusters.RData', list = c('clusters', 'clusters_info'))

# load calculated clusters
load('../data/clusters.RData')

p <- ggplot(clusters_info, 
            aes(x = x_tsne_coordinate, y_tsne_coordinate,  
                label1 = step_index, label2 = A1, label3 = A2, label4 = A3,
                label5 = A4, label6 = A5, label7 = A6, label8 = A7, label9 = A8, label10 = A9)) + 
  geom_point(aes(colour = class))
ggplotly(p)
```

